\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-14 papers/jss/article.Rnw
Dirk likes my tongue in cheek subtitle for the intro so change the section title to "Introduction: Friends don't let friends use CSV".
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@784 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Introduction}

@@

<<echo=FALSE,fig=TRUE>>=
require(RProtoBuf)
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("/tmp/hist.pb")
plot(as.histogram(hist))
@

>>>>

\section{Introduction: Friends don't let friends use CSV}

@@

<<echo=FALSE,fig=TRUE>>=
require(RProtoBuf)
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("hist.pb")
plot(as.histogram(hist))
@
